---
title: "GeoSocial - cookbook"
output: pdf_document
params:
  msg0: NA
  msg1: NA
  msg2: NA
  msg3: NA
  msg4: NA
  msg5: NA

---

          
```{r,echo=FALSE,purl=FALSE}
# execute code if the date is later than a specified day
do_it = Sys.Date() > '2018-02-14'
```


```{r eval=TRUE,echo=FALSE,purl=FALSE}
#x = rnorm(100)
#print(x)
```
Thank you for using the GeoSocial solution. We created an R script to link data based on the previous questionary. This document thoroughly explains each code and stage of the data linkage process.

`r params$msg0`  

`r params$msg1`  

`r params$msg2`

`r params$msg3`

`r params$msg4`

`r params$msg5`

The R script starts clean the environment, and install the Toolboox and the necessary dependencies. 

```{r,eval=FALSE, comment=NA}
#############################################################################################
########################################    MAIN    #########################################
#############################################################################################
########### ----------- Clean all variables -------- #####
rm(list=ls())

#### ------- Install dependencies ------ ####
path = getwd()
#### ---- Inside the folder: ---- ###
setwd(paste0(path,'/IRISS'))
source('tools/install.R')

#### ----- Compile documentation ---- ##
devtools::document()
devtools::build_manual()
#### ----- Install the IRISS library ----- ####
setwd(path)
#### ----- After generate changes in the library we need to delete it and reinstall ---- ####
remove.packages('IRISS')
install.packages('IRISS',repos = NULL, type = 'source')
```

After the installation of the library, the code would load the library and the parameters file created based on the previous questionary. In addition, the code would created the necessary folders where outputs would be stored. 
```{r,eval=FALSE, comment=NA}
library(IRISS)
########## ------- Load parameters --------- ###### 
LoadParameters(file = "Parameters.json")
##### ------ Create folders ------ #####
CreateFolders()
# #### ------ Create log file ------ #####
# logNm <- 'test.log'
# GenerateLog(name = logNm)
```

In addition, this part of the code run

```{r,eval=FALSE, comment=NA}


######### ---------- A vector with the path of each file ------- @@@@@@@@@@
LSAY_cohort = ParsingParameter('LSAY_cohort')
LSAY_waves = as.numeric(ParsingParameter('LSAY_waves'))
SurveyFiles = ParsingParameter('SurveyFiles')
TSP_year = ParsingParameter('TSP_year')
TSP_variables = ParsingParameter('TSP_variables')

####### -------------- 1. Loading data ----------- #########
###### -------- Load LSAY ------- ####
LSAY_2009 = LoadLSAY(wave = LSAY_waves,cohort = LSAY_cohort)
##### ---- Extract survey responses --- #####
SurveyResponses = LSAY_2009[['SurveyResponses']]
##### ---- Exctract GeospatialResponses --- #####
GeospatialResponses = LSAY_2009[['GeospatialResponses']]

### -------- Load TSP 2021  -------- #######
TSP_2021 = LoadTSP2021(year=LSAY_waves,variables = TSP_variables)
### -------- Extract data ------ #####
TSP_2021_data = TSP_2021[['data']]
### -------- Extract metada ------ #####
TSP_2021_metadata = TSP_2021[['metadata']]

####### -------------- 2. Geospatial data linkage ----------- #########
####### ----------- 2.1 POAS TO SA3 ----------- ######
SurveyResponses_SA3 = LSAY_POA_SA3(data=GeospatialResponses,concordances=concordances)
###### --------- SA3 ------- ########
SurveyResponses_SA3_IN = SurveyResponses_SA3[['sa3']]
###### --------- ABS Metric ------- ########
SurveyResponses_SA3_metric = SurveyResponses_SA3[['metric']]
###### --------- ABS Concordances ------- ########
SurveyResponses_SA3_concordances= as.data.frame(SurveyResponses_SA3[['concordances']])
###### --------- ABS Ratio ------- ########
SurveyResponses_SA3_ratio = as.data.frame(SurveyResponses_SA3[['ratio']])

####### ----------- STAGE 2.2: SA3 TO SA3 year ----------- ######
SurveyResponses_SA3_TSP = LSAY_PSA3_SA3(data=SurveyResponses_SA3_IN,concordances=concordances,year_out = TSP_year)
###### --------- SA3 ------- ########
SurveyResponses_SA3_TSP_OUT = SurveyResponses_SA3_TSP[['sa3']]
###### --------- ABS Metric ------- ########
SurveyResponses_SA3_TSP_metric = SurveyResponses_SA3_TSP[['metric']]
###### --------- ABS Concordances ------- ########
SurveyResponses_SA3_TSP_concordances = as.data.frame(SurveyResponses_SA3_TSP[['concordances']])
###### --------- ABS Ratio ------- ########
SurveyResponses_SA3_TSP_ratio = as.data.frame(SurveyResponses_SA3_TSP['ratio'])

####### ------- GeoSpatial join ------ #####
DataJoined = GeoSpatialJoin(year=LSAY_waves,GeospatialResponses=SurveyResponses_SA3_TSP_OUT,SurveyResponses=SurveyResponses,TSP_data = TSP_2021_data,TSP_metadata = TSP_2021_metadata)

############ --------- Geospatial report --------- ############
summaryResults = SummaryReport(concordances_POA= SurveyResponses_SA3_concordances,
                               concordances_SA3 = SurveyResponses_SA3_TSP_concordances,
                               metrics_POA = SurveyResponses_SA3_metric,
                               metrics_SA3 = SurveyResponses_SA3_TSP_metric)

######## -------- Write the summary report --------- #######
openxlsx::write.xlsx(x=summaryResults,file='outputs/Summary.xlsx')

####### ------- Write stata ------ #####
WriteStata(DataJoined = DataJoined,SurveyResponses = SurveyResponses,output_path = '/Users/gonzalezge/Downloads/', year=LSAY_waves)

```


